MT @HanBaldwin: Fightin OOVs in German \#twitter

### 2013-08-12 darmstadt_gscl_2013/article_twitter_normalization.tex
f-score added for twitter specific stuff

\begin{table}
  \caption{Precision, recall and F1 score for replacement of
    Twitter-specific phenomena\label{table:tw-phenomen-metrics}}
  \begin{tabular}{*{4}{>{\centering\arraybackslash}p{0.25\textwidth}}}
    \hline\noalign{\smallskip}
    OOV subclass & Precision & Recall & F1 score\\\hline
    @-tokens & 0 & 0 & 0\\
    hashtags & 0 & 0 & 0\\
    links & 0 & 0 & 0\\
    e-mail addresses & 0 & 0 & 0\\
    smileys & 0 & 0 & 0\\
    \noalign{\smallskip} \hline
  \end{tabular}
\end{table}

>>>>

\begin{table}
  \caption{Precision, recall and F1 score for replacement of
    Twitter-specific phenomena\label{table:tw-phenomen-metrics}}
  \begin{tabular}{*{4}{>{\centering\arraybackslash}p{0.25\textwidth}}}
    \hline\noalign{\smallskip}
    OOV subclass & Precision & Recall & F1 score\\\hline
    attoken & 98.87 & 98.87 & 98.87\\
    link & 99.44 & 100.00 & 99.72\\
    smiley & 93.79 & 76.26 & 84.12\\
    \noalign{\smallskip} \hline
  \end{tabular}
\end{table}
